Let $\mathcal{A}$ be a \emph{good} category (abelian/exact/triangulated). The precise meaning of this will have to be clarified later (probably, the recent Nakaoka-Palu's paper is the right setting). But, whatever the choice, two things should happen. First, idempotents should split in $\mathcal{A}$. Secondly,  each torsion pair considered  in $\mathcal{A}$ should be functorial on both sides. If $(\mathcal{T},\mathcal{F})$ is such a torsion pair, we will denote by $t:\mathcal{A}\longrightarrow\mathcal{T}$ (resp. $f:\mathcal{A}\longrightarrow\mathcal{F}$) the right (resp. left) adjoint of the inclusion functor and, also, the composition $\mathcal{A}\stackrel{t}{\longrightarrow}\mathcal{T}\stackrel{i}{\hookrightarrow}\mathcal{A}$ (resp. $\mathcal{A}\stackrel{f}{\longrightarrow}\mathcal{F}\stackrel{j}{\hookrightarrow}\mathcal{A}$), where $\mathcal{T}\stackrel{i}{\hookrightarrow}\mathcal{A}$
(resp. $\mathcal{F}\stackrel{j}{\hookrightarrow}\mathcal{A}$) is the inclusion functor. The functoriality should then give rise to an admissible sequence $t(M)\longrightarrow M\longrightarrow f(M)$, for each object $M\in\mathcal{A}$ (e.g. if $\mathcal{A}$ is abelian, that sequence should be short exact, if $\mathcal{A}$ is exact it should be a conflation, if $A$ is triangulated it should be a triangle).



$\mathcal{W}$ a full subcategory of $\mathcal{A}$ closed by direct summands and extensions, and consider the category $\underline{\mathcal{A}}=\dfrac{\mathcal{A}}{\mathcal{W}}$.

Let $(\mathcal{X},\mathcal{Y})$ be a orthogonal pair in $\underline{\mathcal{A}}$ and consider the following classes in $\mathcal{A}$:
\begin{align*}
  \mathcal{T} &= \{ T\in\mathcal{A} | \underline{T}\in\mathcal{X} \} \\
  \mathcal{F} &= \{ F\in\mathcal{A} | \underline{F}\in\mathcal{Y} \}.
\end{align*}

\begin{lemma}
  In the previous notation, $(\mathcal{T}, \mathcal{T}^\perp)$ is a orthogonal pair.
\end{lemma}

\begin{proof}
  In order to prove it we need to show that $^\perp(\mathcal{T}^\perp) = \mathcal{T}$.

  Let $M\in {^\perp(\mathcal{T}^\perp)}$, this means that
  \begin{equation}
    \mathcal{A}(M,Y) = 0
  \end{equation}
  whenever
  \begin{equation}
    \mathcal{A}(T,Y) = 0\,\forall T\in\mathcal{T}.
  \end{equation}

  However, if $\mathcal{A}(T,Y)=0$ $\forall T\in\mathcal{T}$, then $\underline{\mathcal{A}}(\underline{X},\underline{Y})=0$ $\forall \underline{X}\in\mathcal{X}$. Hence, $\underline{Y}\in\mathcal{Y}$.
  So $\underline{\mathcal{A}}(\underline{M},\underline{Y})=0$ $\forall \underline{Y}\in\mathcal{Y}$. Hence, $\underline{M}\in\mathcal{X}$ and so $M\in\mathcal{T}$.

  We have proved that $^\perp(\mathcal{T}^\perp) \subseteq \mathcal{T}$, the converse inclusion is trivial.
\end{proof}

\begin{rmk}
  The dual statement holds for $\mathcal{F}$. Notice that have we also proved that if $\mathcal{A}(T,Y)=0$ $\forall T\in\mathcal{T}$, then $\underline{Y}\in\mathcal{Y}$ and hence $Y\in\mathcal{F}$. That is, $\mathcal{T}^\perp \subseteq \mathcal{F}$ and dually $^\perp\mathcal{F}\subseteq \mathcal{T}$.
\end{rmk}

\sepline

\bf Properties of $(\mathcal{T},\mathcal{T}^\perp)$ and $(^\perp\mathcal{F},\mathcal{F})$: \rm
\begin{enumerate}
  \item $^\perp\mathcal{F}\subseteq\mathcal{T}$ and $\mathcal{T}^\perp\subseteq \mathcal{F}$.
  \item $\mathcal{T}\cap\mathcal{F} = \mathcal{W}$.
  In fact, $M\in\mathcal{T}\cap\mathcal{F}$ iff $\underline{M}\in\mathcal{X}\cap\mathcal{Y}=0$, which happens iff $M<_\oplus W$ for some $W\in\mathcal{W}$,
  but $\mathcal{W}$ is closed by direct summands, hence $M\in\mathcal{W}$.
  \item If $N\in\mathcal{T}^\perp \cap{^\perp\mathcal{F}}$, then $N=0$. It follows from $N\in\mathcal{T}^\perp \cap{^\perp\mathcal{F}}\subseteq\mathcal{F}\cap\mathcal{T}=\mathcal{W}$. But $\mathcal{W}\subseteq\mathcal{T}$, hence $\mathcal{A}(W',N)=0$ $\forall W'\in\mathcal{W}$,
  in particular $\mathcal{A}(N,N)=0$, i.e. $N=0$.
\end{enumerate}

\sepline

If $\mathbb{t}=(\mathcal{T},\mathcal{F})$ is a orthogonal pair in a cocomplete and locally small abelian category $\mathcal{A}$, then $\mathbb{t}$ is a torsion pair. Indeed, if $M$ is any object and we consider the set $\mathcal{T}_M$ of subobjects of $M$ which are in $\mathcal{T}$, then $t(M):=\sum_{T\in\mathcal{T}_M}T$ is subobject of $M$ which is an epimorphic image of $\coprod_{T\in\mathcal{T}_M}$ and, hence, we have that $t(M)\in\mathcal{T}_M$.
If we had a nonzero morphism $f:T'\longrightarrow M/t(M)$, where $T'\in\mathcal{T}$, then we would have that $\text{Im}(f)=\tilde{T}/t(M)$ is a nonzero submodule of $M/t(M)$ which is in $\mathcal{T}$. Since $\mathcal{T}$ is closed under extensions and we have an exact sequence $0\rightarrow t(M)\longrightarrow\tilde{T}\longrightarrow \tilde{T}/t(M)\rightarrow 0$, we conclude that $\tilde{T}\in\mathcal{T}$. But then we have that $\tilde{T}\in\mathcal{T}_M$, which is a contradiction since $t(M)$ contains all subobjects in $\mathcal{T}_M$.

\sepline

\begin{lemma}
  Let $(\mathcal{T}_1,\mathcal{F}_1)$ and $(\mathcal{T}_2,\mathcal{F}_2)$ be torsion pairs in $\mathcal{A}$, with associated radical functors $t_i$ and coradical functors $f_i$ ($i=1,w$), respectively. Suppose that they satisfy the following conditions:
    \begin{enumerate}
    \item[a)] $\mathcal{T}_2\subseteq\mathcal{T}_1$ (equivalently, $\mathcal{F}_1\subseteq\mathcal{F}_2$)
    \item[b)] $\mathcal{T}_2\cap\mathcal{F}_1=0$.
    \item[c)] $ $
    \end{enumerate}
    If we put $\mathcal{W}=\mathcal{T}_1\cap\mathcal{F}_2$. Then the following assertions hold:

    \begin{enumerate}
    \item $\mathcal{T}_1$ consists of those objects $X\in\mathcal{A}$ such that $f_2(X)\in\mathcal{W}$. We will write $\mathcal{T}_1=\mathcal{T}_2\star\mathcal{W}$.
    \item $\mathcal{F}_2$ consists of those objects $Y\in\mathcal{A}$ such that $t_1(Y)\in\mathcal{W}$. We will write $\mathcal{F}_2=\mathcal{W}\star\mathcal{F}_1$.
    \end{enumerate}

\end{lemma}

\begin{proof}
We just prove assertion 1, and assertion 2 will follow by duality.
Let us take $X\in\mathcal{T}_2\star\mathcal{W}$. Since we have an admissible sequence $t_2(X)\longrightarrow X\longrightarrow f_2(X)$ whose outer terms are in $\mathcal{T}_2$ and $\mathcal{W}$, respectively, and these two classes are contained in $\mathcal{T}_1$ we conclude that $\mathcal{T}'_1\subseteq\mathcal{T}_1$, because $\mathcal{T}_1$ is closed under taking extensions in $\mathcal{A}$.



  Let $T_1$ be in $\mathcal{T}_1$ and consider its canonical admissible sequence

  \begin{equation}
    t_2(T_1)\to T_1\nto{f} f_2(T_1).
  \end{equation}
    Note that $\underline{f}=0$ because of condition c) in the statement. It follows that $f$ decomposes  in the form $f:T_1\stackrel{\gamma}{\longrightarrow}W\stackrel{\phi}{\longrightarrow}f_2(T_1)$, where $W\in\mathcal{W}$. We then consider the following admissible pullback diagram
  \begin{equation}
    \begin{tikzcd}
      t_2(T_1)\arrow{r}\arrow[equal]{d} &
        \widehat{T}_1\arrow{r}\arrow{d} &
          W\arrow{d}{\phi}\\
      t_2(T_1)\arrow{r}&
        T_1\arrow{r}{f}&
          f_2(T_1)
    \end{tikzcd}
  \end{equation}


  Then, there exist a (non necessarely unique) $\eta:T_1\to \widehat{T}_1$ making the following diagram commute.

  \begin{equation}
    \begin{tikzcd}
      T_1\arrow[bend right]{ddr}[']{1}\arrow[dashed]{dr}{\eta}\arrow[bend left]{rrd}{\gamma}&&\\
      &
        \widehat{T}_1\arrow{r}\arrow{d}&
          W\arrow{d}{\phi}\\
      &
        T_1\arrow{r}{f}&
          f_2(T_1)
    \end{tikzcd}
  \end{equation}

  Hence, $T_1 <_\oplus \widehat{T}_1\in \mathcal{T}_2  \ast \mathcal{W}$. This implies that  $\mathcal{T}_1\subseteq \mathrm{add}(\mathcal{T}_2\ast \mathcal{W})$. The proof will be finished once we check that $\mathcal{T}_2\ast \mathcal{W}$ is closed under direct summands. But this is a direct consequence of the functoriality of the torsion pair.
  Indeed if we have admissible torsion sequences $t_2(M)\longrightarrow M\longrightarrow f_2(M)$ and $t_2(N)\longrightarrow N\longrightarrow f_2(N)$, then the coproduct sequence $t_2(M)\oplus t_2(N)\longrightarrow M\oplus N\longrightarrow f_2(M)\oplus f_2(N)$ is the admissible torsion sequence for $M\oplus N$. The fact that $M\oplus N\in\mathcal{T}_2\ast \mathcal{W}$ is then equivalent to the fact that $f_2(M)\oplus f_2(N)\in\mathcal{W}$. Since $\mathcal{W}$ is closed under direct summands, we conclude that $f_2(M)\in\mathcal{W}$ and, hence, that $M\in\mathcal{T}_2\ast\mathcal{W}$.

\end{proof}
